A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-04-16 manuscript.Rmd
streamline internal dependency

A preregistration serves as a tool that may help to increase the credibility of empirical results.
Without getting lost in the meta scientific arguments for preregistration, we want to note two advantages.
First, a preregistration is an opportunity to carefully plan a study.
Gathering empirical data often requires enormous resources and better planning increases the chances that these efforts are worthwhile.
For us a good preregistration is the same as a good plan; the only difference is that a preregistration is made public beforehand.
Some [citation!] argue that preregistration can not fulfill its promise to reduce the false discovery rate of science, if we allow to deviate from them.
While such argument has some merits, we believe another advantage of preregistration is transparency.
If researchers deviate from their preregistration, they probably have good reason to do so, which means they have learned something from the process of conducting the study.
A preregistration, together with version control allows their readers to inform themselfs about these lessons learned.

@@

First dependency management, which means that you capture the interrelations between the components of your analysis.
You cannot run an analysis without data, you cannot render a dynamic document without an analysis, and so forth.
Understanding these relations is often key to reproducing a project.
A reader of your reproducible manuscript should be able to derive how they are to reproduce it (ideally by a statement in your [README]).
The "components" of an analysis are often loosely mapped onto files.
For a simple project it might be enough to have a single R Markdown.
However, while it is easy to understand how to reproduce the end result, this approach quickly gets unwieldy.
To better navigate the data analysis, a researcher often splits it across several scripts.
For example, they create a script to load the data and another to run the analysis.
This modularisation facilitates reuse, because the loading script may be used by other projects building on the same data, while the analysis script may be employed on other data and so forth.
The downside is that reproducibility is complicated, because instead of reproducing everything in one step, multiple steps are required.

>>>>

A preregistration serves as a tool that may help to increase the credibility of empirical results.
Without getting lost in the meta scientific arguments for preregistration, we want to note two advantages.
First, a preregistration is an opportunity to carefully plan a study.
Gathering empirical data often requires enormous resources and better planning increases the chances that these efforts are worthwhile.
For us a good preregistration is the same as a good plan; the only difference is that a preregistration is made public beforehand.
Some [citation!] argue that preregistration can not fulfill its promise to reduce the false discovery rate of science, if we allow to deviate from them.
While such argument has some merits, we believe another advantage of preregistration is transparency.
If researchers deviate from their preregistration, they probably have good reason to do so, which means they have learned something from the process of conducting the study.
A preregistration, together with version control allows their readers to inform themselves about these lessons learned.

@@

A reader of your reproducible manuscript should be able to derive how they are to reproduce it (ideally by a statement in your [README]).
To be able to do that, it is often key to understand how different components of the project relate to each other.
You cannot run an analysis without data, you cannot render a dynamic document without an analysis, and so forth.
Dependency management means that you capture the interrelations between the components of your analysis.
The "components" of an analysis are often loosely mapped onto files.
For a simple project it might be enough to have a single R Markdown.
However, while it is easy to understand how to reproduce the end result, this approach quickly gets unwieldy.
To better navigate the data analysis, a researcher often splits it across several scripts.
For example, they create a script to load the data and another to run the analysis.
This modularisation facilitates reuse, because the loading script may be used by other projects building on the same data, while the analysis script may be employed on other data and so forth.
The downside is that reproducibility is complicated, because instead of reproducing everything in one step, multiple steps are required.
